---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# famnet

[![Travis build status](https://travis-ci.org/lwjohnst86/famnet.svg?branch=master)](https://travis-ci.org/lwjohnst86/famnet)
[![Coverage status](https://codecov.io/gh/lwjohnst86/famnet/branch/master/graph/badge.svg)](https://codecov.io/github/lwjohnst86/famnet?branch=master)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

The goal of famnet is to characterize a family network, based on having an
individual's ID, and their mother's and father's ID.

# Installation

Install the developmental version.

```{r install, eval=FALSE}
# install.packages("remotes")
remotes::install_github("lwjohnst86/famnet")
```

# Usage

You can use the famnet functions to determine family relation links. For instance,
say you a dataset like this:

```{r}
library(famnet)
head(fmn_df)
tail(fmn_df)
```

And you want to determine sibling relations. You can use:

```{r}
library(famnet)
fmn_siblings(fmn_df, "PersonID", "MotherID", "FatherID")
```

Which indicates all the sibling connections in the `fmn_df` dataset.
